---
title: 'Time series models for ecologists: course pre-requisites'
author: "Andrew Parnell"
output:
  pdf_document: default
  html_document: default
---

In preparation for the course please install the following, preferably in the below suggested order.

Remember you will need to bring your own personal computer for the duration of the course.

### Step 1

Install the following using the corresponding links

-	R: [http://www.r-project.org](http://www.r-project.org)

-	Rstudio (optional but recommended): [https://www.rstudio.com](https://www.rstudio.com)

-	JAGS: [http://mcmc-jags.sourceforge.net](http://sourceforge.net/projects/mcmc-jags/files/)

### Step 2

Now install the following packages by going into Rstudio (or R) and typing:
```{r,eval=FALSE}
install.packages(c('R2jags', 
                   'rjags', 
                   'lubridate', 
                   'tidyverse', 
                   'forecast'))
```

### Step 3

Install `rstan` by going to this [link](https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started) and following the instructions for your operating system.

### Step 4

Check that JAGS works by going to a command line terminal and typing `jags`. If it opens successfully type `exit`. 

Now go into R and copy and paste the following text:
```{r,eval=FALSE}
library(R2jags)
model_code="
model {
  y ~ dnorm(mu,1)
  mu ~ dnorm(0,1)
}
"
model=jags(data=list(y=1),
           model.file=textConnection(model_code),
           parameters.to.save = 'mu',
           n.chains=1)
plot(model)
```
This should produce a plot.

### Troubleshooting

If you run into any problems please drop us a line at <andrew.parnell@ucd.ie>.

